\iffalse 
\section{Boundary or Initial Value Problems}
When working with ODE's,
whether a problem explicitly states the boundary conditions 
or the initial values does not affect whether a problem can be solved.
When working with 
PDE's that is no longer the case. The different types 
of PDE's demand differently posed problems. 


----THE ABOVE\@: SKAL DET OVERHOVEDET MED?----
\fi

The theory of FEM stems from elliptic PDE's, so we will start by
describing these problems for elliptic PDE's.
We will use a second order elliptic partial differential operator $L$ as 
\begin{equation}
    Lu = - \sum_{i,k=1}^n \partial_i(a_{ik} \partial_k u)+ a_0u.
    \label{eq:Lu}
\end{equation}
The ellipticity requirement in Definition \ref{def:pde_classification} only 
makes demands on the coefficients for the second order partial derivatives, 
and we will ignore the other parts for now. Unless otherwise stated, $L$ is 
always defined as here.
\iffalse
We therefore assume that we can write a general linear PDE of second 
order with $n$ variables as 
\begin{equation*}
    Lu = f.
\end{equation*}
\fi
Since we are trying to solve the PDE over some space $\Omega$, we write
\begin{align}
\begin{split}
    Lu &= f \quad \text{in } \Omega \label{eq:b_v_problem} \\
    u &= g \quad \text{on } \partial \Omega.
\end{split}
\end{align}
A boundary condition on the form (\ref{eq:b_v_problem}) is called a 
Dirichlet condition, which is when $u$ is specified on the boundary. 
If $u=0$ we have homogeneous boundary conditions, which we usually assume 
to make things easier. If that is not the case, we can
transform the problem. To do this, we assume there exists a function 
$\tilde{u}$ such that $\tilde{u}=g$ on $\partial \Omega$. Then we define 
$w = u - \tilde{u}$ and $\tilde{f}=f-L\tilde{u}$ and we get that
\begin{align}
\begin{split}
    Lw &= \tilde{f} \quad \text{in } \Omega \label{eq:b_v_problem_homogeneous} \\
    w &= 0 \quad \text{on } \partial \Omega. 
\end{split}
\end{align}
To make these explicit demands for $u$ on $\partial \OO$ can 
be rather restrictive.
Instead we can make implicit restrictions, by constraining 
$\partial _i u$ on $\partial \OO$.
This will be dealt with later.