\section{Neumann Boundary Conditions}
We now require $a_0(x)$ in the Elliptic PDE to be bounded from below by a positive number. 
Inequality~\eqref{eq:alpha_ellipticity} will also be true for smaller $\alpha$, so if 
necessary we can reduce it, and assume 
\begin{equation*}
  a_0(x) \geq \alpha >0 \quad \forall x \in \OO.
\end{equation*}
This gives us the lower bound on $a$ as 
\begin{equation*}
   a(v,v)  \geq \alpha |v|^2_1 + \alpha \|v\|^2_0 = \alpha \|v\|^2_1 \quad \forall v \in H^1(\OO).
\end{equation*}
We can therefore assume from this point on that $a$ is $H^1$ elliptic.

\begin{defn}{Neumann Boundary condition}
    Let $\frac{\partial u}{\partial \mathbf{n}}= \mathbf{n}\cdot \nabla u$ be the normal derivative. Then the Neumann boundary condition is given by
    \begin{equation}
        \frac{\partial u}{\partial \mathbf{n}}  = g\quad \text{on } \partial \Omega.
    \end{equation}
\end{defn}
With this definition, we can start looking at the existence of solutions to problems which are defined using this type of condition.
\input{Afsnit/Kapitel1/sætninger/neumann_bc_løsning_eksistens.tex}
Using this definition, we can look at the Poisson equation with Neumann boundary conditions. Thus
\begin{align}
\label{eq:Neumann_Poisson}
\begin{split}
    -\Delta u &= f \quad \text{in } \Omega, \\
    \frac{\partial u}{\partial \mathbf{n}} &= g \quad \text{on } \partial \Omega.
\end{split}
\end{align}
Due to the fact that~\eqref{eq:Neumann_Poisson} only contains derivatives with respect to $u$,
 additive constants independent of $u$ are unimportant.
Thus if $u$ satisfies~\eqref{eq:Neumann_Poisson}, then $u + c$ also satisfies~\eqref{eq:Neumann_Poisson} for any constant $c$.
This means that the solution to~\eqref{eq:Neumann_Poisson} is only unique up to a constant,
 which extends to other equations with Neumann boundary conditions.

It turns out that we can formulate the weak form of this problem by restricting to the subspace $V=\{v\in H^1(\Omega):\int_{\Omega}vdx=0\}$.
Define $a(u,v) = \int_\OO \nabla u \cdot \nabla v dx$. Examining a version of 
the Friedrich inequality, Theorem~\ref{thm:friedrich}, which can be found on 
page 46 of~\cite{Braess}, $a$ can be found to be $V$-elliptic.
We now want to assert that every classical solution to the variational problem in Theorem~\ref{thm:neumann_solution_existence} satisfies~\eqref{eq:Neumann_Poisson}.
To do this, we let $w=\nabla u$. Thus~\eqref{eq:Neumann_Poisson} can be written as
\begin{align}\label{eq:Neumann_Poisson_weak}
\begin{split}
    -\text{div } w &= f \quad \text{in } \Omega, \\
    \mathbf{n}^T w &= g \quad \text{on } \partial \OO.
\end{split}    
\end{align}
From the Gauss Integral Theorem, we have that
\[\int_{\Omega} \text{div } w dx = \int_{\partial \OO} \mathbf{n}^T w ds.\]
Then from~\eqref{eq:Neumann_Poisson_weak} we get
\begin{align}
\begin{split}
%\int_{\Omega} \text{div } w dx &= \int_{\partial \OO} \mathbf{n}^Tw ds \\ 
\int_{\Omega} -f dx &= \int_{\partial \OO} g ds.
\end{split}
\end{align}
Since $V$ by construction is a closed and linear subspace of a Hilbert space, 
V is complete with respect to the norm, and is therefore also a Hilbert space. 
We can then use Corollary~\ref{cor:lax_milgram} 
 and get $u\in V$, where %TODO skal vi uddybe hvorfor $V$ er closed (kig på Cauchy følger) & Linear
\begin{equation}\label{eq:Lax-Milgram_Neumann}
  a(u,v) = {(f,v)}_{0,\Omega} + {(g,v)}_{0,\partial \OO} \quad \forall v\in V.  
\end{equation}
Equation~\eqref{eq:Neumann_Poisson} has now been shown to be true for 
every classical solution of the variational problem for $u\in V$. However, for some 
$u\in H^1(\OO)\setminus V$, we can use the following construction for 
the constant $c$:
\begin{equation*}
    \forall f \in H^1(\OO): \,\, c = \frac{\int_\OO f(x) dx }{\int_\OO 1 dx}.
\end{equation*}
Define $v(x) = f(x) - c$, and then 
\begin{equation*}
    \int_\OO v(x)dx = \int_\OO f(x) dx - c\int_\OO 1 dx = \int_\OO f(x) dx - \frac{\int_\OO f(x) dx }{\int_\OO 1 dx} \int_\OO 1 dx = 0,
\end{equation*}
so $v \in V$. For every $u\in H^1(\OO)\setminus V$ we can find a fitting 
constant such that $u+c \in V$. Every classical solution of the 
variational problem corresponding to a Neumann Boundary condition therefore 
satisfies \eqref{eq:Neumann_Poisson}, and \eqref{eq:Neumann_Poisson} becomes the weak formulation.