This chapter is based on~\cite{Braess}.
The theory of Finite Element Method (FEM) stems from a 
wish to solve Partial Differential Equations (PDE's),
which may or may not be analytically solvable. 
To do this we will introduce various kind of PDE's, 
the type of
problems, and examine the spaces containing solutions. 
The functions used in this chapter wil be of $n$ 
variables and $\Omega$ will be 
an open subset of $\RR^n$ with a piecewise smooth boundary.
The first PDE we introduce is a second order PDE and as 
such has the form
\begin{equation}
	 c(x) u + \sum_{i=1}^{n}b_i(x)u_{x_{i}}
	- \sum_{i,k=1}^{n}a_{ik}(x)u_{x_i x_k}\label{eq:pde_order2_n}
	= f(x).
\end{equation}

The coefficients in (\ref*{eq:pde_order2_n}) can be 
organized nicely in a vector containing every $b_i$ 
in $b(x)$
and a matrix $A(x)$ containing every $a_{ik}$.
Assuming $u$ in (\ref*{eq:pde_order2_n}) is sufficiently 
smooth, then $u_{x_i x_k} =u_{x_k x_i} $, and we can 
assume without loss of generality $A(x)$ is 
symmetric. %? Passer dette bedre?
We use $A(x)$ to define the type of equation we are working 
with and therefore to characterize the problem we are 
working with.
\begin{defn}{Classification of a PDE}
	The Equation (\ref{eq:pde_order2_n}) is classified as follows:
	\begin{itemize}
		\item Elliptic at $x$, if $A(x)$ is positive definite
		\item Hyperbolic at $x$, if $A(x)$ has one negative and $n-1$ postive eigenvalues
		\item Parabolic at $x$, if $A(x)$ is positive semidefinite, not positive definite, and rank$([A(x), b(x)])=n$
	\end{itemize}
	If for a given equation the above conditions hold for all points of the domain, the equation is called elliptic, hyperbolic or parabolic respectively.\label{def:pde_classification}
\end{defn}


\begin{exmp}
The PDE $c(x)u + u_{x_1x_1} + u_{x_2x_2}$ is an example of a simple Elliptic PDE, since
\begin{equation}\label{eq:Basic matrix}
	A(x) = \begin{bmatrix}
		1 & 0\\
		0 & 1
	\end{bmatrix}, \quad
	b(x) = \begin{bmatrix}
		0 & 0\\
		0 & 0
	\end{bmatrix}
\end{equation}

Had entry $a_{11}$ been negative, the PDE would have been Hyperbolic, since the eigenvalues would be $-1$ and $1$. To convert~\eqref{eq:Basic matrix} to matrices for a Parabolic PDE, we can simply change $a_{11}$ to $0$, which results in $A(x)$ being positive semidefinite and $\text{rank}([A(x), b(x)]) = 2 = n$.
\end{exmp}
	

This chapter will work with several different spaces, and with different norms and 
seminorms. 
These norms are defined in~\cite{Braess} and in the List of Symbols. 
The spaces in which these norms are from should be obvious from context, but from 
time to time a space will be included in the subscript to specify exactly which 
space the norm is from.