\input{Afsnit/Kapitel1/friedrich.tex}
Theorem~\ref{thm:friedrich} and Corollary~\ref{cor:friedrich_n} both deal with 
functions which are zero on the boundary. 
This is restrictive, and we would like to be able to examine 
functions which are not zero on the boundary.
To remedy this, we introduce the Trace Theorem, which requires the cone condition, which we now define.
\input{Afsnit/Kapitel1/Cone_condition.tex}
With Definition~\ref{def:cone_condition}, we can proceed to the Trace Theorem.
\input{Afsnit/Kapitel1/sætninger/Trace_Theorem.tex}
Theorem~\ref{thm:trace} guarantees that functions which are not 
zero on the boundary are at least an $L_2$ function, and as such are bounded. %TODO Kig efter Anton rettelser
\subsection{Attributes of Solutions}
By rephrasing the problems to the form shown in the 
following theorem,
the equality in the theorem can be used to find solutions. %TODO Kig igen, når Antons svar er rettet
\input{Afsnit/Kapitel1/sætninger/Charac_Theorem.tex}
To use Theorem~\ref{thm:charac_theorem}, we
only make assumptions on the linearity of the space, however we
do not guarantee the existence  of solutions, only their characterization.
It is possible to set up a variational problem such that $J$ does 
not attain its minimum.
To engage with the existence of solutions, we make more assumptions on 
the space in which we work.
We start by specifying the bilinear form in Theorem~\ref{thm:charac_theorem}.
\begin{defn}{\quad}
   Let $H$ be a Hilbert space. A bilinear form $a : H \times H \to \RR$ is 
   called continuous if there exists some $C > 0$ such that 
   \begin{equation}
    |a(u,v)| \leq C \|u\|\, \|v\| \quad \forall u,v \in H.
   \end{equation} 
   If a bilinear form $a$ is symmetric and continuous, and there exists som $\alpha >0$ such that 
   \begin{equation*}
    a(v,v) \geq \alpha \|v\|^2 \quad \forall v \in H,
   \end{equation*}
   $a$ is called elliptic.\label{def:elliptic}
 \end{defn}
From this point forward $a$ will be referring to the bilinear form given by
\begin{equation}
   a(u,v) = \int_\Omega \left[\sum_{i,k} a_{ik}\partial_i u\partial_k v+a_0uv\right]dx,
\end{equation}
unless otherwise stated.
%TODO Beskriv hvorfor en elliptic diff operator giver en elliptic a

\section{Homogeneous Dirichlet Conditions}
Since we are trying to solve the PDE over some space $\Omega$, we write
\begin{align}
\begin{split}
    Lu &= f \quad \text{in } \Omega \label{eq:b_v_problem} \\
    u &= g \quad \text{on } \partial \Omega.
\end{split}
\end{align}
A boundary condition on the form~\eqref{eq:b_v_problem} is called a 
Dirichlet condition, which is when $u$ itself is specified on the boundary. 
If $u=0$ on the boundary we have homogeneous boundary conditions, which we usually assume 
to make things easier. If that is not the case, we can
transform the problem. To do this, we assume there exists a function 
$\tilde{u}$ such that $\tilde{u}=g$ on $\partial \Omega$. Then we define 
$w = u - \tilde{u}$ and $\tilde{f}=f-L\tilde{u}$ and we get that
\begin{align}
\begin{split}
    Lw &= \tilde{f} \quad \text{in } \Omega \label{eq:b_v_problem_homogeneous} \\
    w &= 0 \quad \text{on } \partial \Omega. 
\end{split}
\end{align}
To make these explicit demands for $u$ on $\partial \OO$ can 
be rather restrictive.
Instead we can make implicit restrictions, by constraining 
$\partial _i u$ on $\partial \OO$.
This will be dealt with later.
%TODO Rettelser mht det forrige

We now use Theorem~\ref{thm:charac_theorem} to show a link between classical 
solutions and solutions of appropriate variational problems.
%TODO Anton ellipticitet rettelser mht a
\input{Afsnit/Kapitel1/sætninger/Minimal_Property.tex}
The same kind of proof can be used to show that a solution $u$ to~\eqref{eq:min_prop_variational_problem} which fulfills 
$u\in C^2(\OO) \cap C^0(\OO)$ is also a classical solution. 
When $u\in C^2(\OO) \cap C^0(\OO)$ the variational problem and 
homogeneous boundary value problem are thusly equivalent.
We can therefore use the variational problem to find solutions, making the
 the following theorem useful.
\input{Afsnit/Kapitel1/sætninger/Lax_Milgram_Thm.tex}
As all Hilbert spaces are vector spaces, they will be convex by definition.
As such, subsets of Hilbert spaces we are going to be working will be as well,
and we can use the following corollary.
\input{Afsnit/Kapitel1/sætninger/Lax_Milgram_Cor.tex}

When working with PDE's the equation shown in Corollary~\ref{cor:lax_milgram} 
is called the variational formulation of a boundary condition problem. 
To find the solution $u$, we split a Hilbert space of functions, $H$, 
into finite dimensional subspaces, and use these to approximate $u$. 
We test this approximatation using test functions, typically from the same subspace,
 using the equality in Corollary~\ref{cor:lax_milgram}, which must be true for all test functions.
This widens the 
space in which we look for solutions.
For example, by using the variational formulation, we can define a weak solution 
which no longer requires $u \in C^2(\OO)$.
\begin{defn}{\quad}
    A function $u\in H_0^1(\OO)$ is called a weak solution of 
    the Dirichlet problem with homogeneous boundary conditions,~\eqref{eq:b_v_problem_homogeneous}, if 
     \begin{equation*}
        a(u,v) = {(\tilde{f},v)}_0 \quad \forall v \in H_0^1(\OO).
     \end{equation*}
     Here $a(u,v)$ is the bilinear from from~\eqref{eq:a(u,v)}, 
     and ${(\tilde{f},v)}_0$ is a linear bounded functional provided $\tilde{f}\in L^2$, and it can therefore be used as $\ell(v)$ in~\eqref{eq:l(v)}.
\end{defn}
A weak solution only requires $u\in H_0^1(\OO)$, and is clearly less strict. 
Thus there is a higher chance of a solution existing for any given problem, 
and is therefore desirable. So we now look at the existence of weak solutions.
\input{Afsnit/Kapitel1/sætninger/existence_theorem.tex}

%TODO Skriv eksempel der kan udvides til inhomogen, og tilhørende tekst

\section{Inhomogeneous Dirichlet Conditions}
%TODO Indledning
We can use Theorem~\ref{thm:existence_hom_dirichlet} to examine the inhomogeneous Dirichlet problem.
We have looked at how a inhomogeneous 
Dirichlet problem could be turned into a homogeneous one, and we will use 
a similar construction here. Recall the inhomogeneous Dirichlet problem, Equation~\eqref{eq:b_v_problem}, and let 
$\tilde{u} \in C^2(\OO)\cap C^0(\bar{\OO}) \cap H^1(\OO)$ be a function such that 
\begin{equation*}
   \tilde{u} = g \quad \text{on } \partial \OO,
\end{equation*}
and $w = u-\tilde{u}$ and $\tilde{f} = f-L\tilde{u}$. We now have the homogeneous 
Dirichlet problem 
\begin{align}
\begin{split}
    Lw &= \tilde{f} \quad \text{in } \Omega,  \\
    w &= 0 \quad \text{on } \partial \Omega. 
\end{split}
\end{align}
By Theorem~\ref{thm:existence_hom_dirichlet},
 a weak solution $w \in H_0^1(\OO)$ exists. As ${(L\tilde{u},v)}_0 = a(\tilde{u},v)$,
we get
\begin{alignat*}{2}
      a(w,v) &= {(\tilde{f},v)}_0 \quad &&\forall v \in H_0^1(\OO) \\
      a(u-\tilde{u},v) &= {(f-L\tilde{u},v)}_0 &&\\
      a(u,v) - a(\tilde{u},v) &= {(f,v)}_0 - (L\tilde{u},v)_0 \quad && \\
      a(u,v) &= {(f,v)}_0. &&
\end{alignat*}
We stil have the condition $u-\tilde{u}=w\in H_0^1(\OO)$, and the weak formulation 
of the inhomogeneous Dirichlet boundary condition can then be written as
\begin{align*}
   a(u,v) = {(f,v)}_0 \quad \forall v &\in H_0^1(\OO) \\
   u-\tilde{u} & \in H_0^1(\OO).
\end{align*}
By Theorem~\ref{thm:c_dense_in_h}, $C^2(\OO)\cap H^1(\OO)$ is dense in $H^1(\OO)$, 
and $C^0(\bar{\OO})\cap H^1_0(\OO)$ 
is dense in $H^1_0(\OO) \subset H^1(\OO)$. Following the same density arguments 
as have been done several times before, it suffices to look at $\tilde{u}\in H^1(\OO)$, however it is not always possible to find an admissible $\tilde{u}$.

%TODO Skridtet fra svage løsninger til at overgå til Neumann
